\begin{center}
    \section*{ABSTRACT}
    \addcontentsline{toc}{chapter}{Abstract}
    \justify
    \begin{doublespace}
        Generative adversarial networks (GANs) is a type of generative model. 
        A GAN consist of two neural networks, a generator network and a 
        discriminator network. The generator outputs data, taking as input a 
        random noise. The discriminator has to classify whether data given as 
        input to it is a real data from the database or a fake one created by 
        the generator. The generator competes against its adversary, the 
        discriminator. As the training for this generative model progresses, 
        the discriminator learns to classify the fake data accurately, while 
        the generator learns to create realistic samples. An equilibrium is 
        reached when the data created by the generator is indistinguishable 
        from real data. GANs are frequently used in image generation and, 
        they produce sharp images too. A downside for GAN is that it does not 
        have a well$-$defined loss function, which makes training GANs 
        difficult. Many variations of GANs have been introduced by 
        researchers all around the globe. GANs are one of the most promising 
        approaches to generative modelling present today and extensive research 
        is being done to explore their potential.
    
    \noindent\textbf{Keywords:} Generative algorithms, Adversarial training
    \end{doublespace}
\end{center}
